### 2023-04-11 definitions.tex
up

\mathieu{ Maybe add this back ?
A {\em labeled transition system} (LTS for short) is a tuple $\mathscr{S}=(S, \Sigma, \rightarrow)$ where 
$S$ is a set of {\em states}, $\Sigma$ is a (finite) set of {\em labels}, and 
${\rightarrow} \subseteq S\times \Sigma \times S$ is a 
ternary relation,
denoted as the set of {\em labeled transitions}. }
\end{definition}

@@

\problemx{$d$-VASS reachability}
{A $d$-Vass $V=(Q,T)$, and configurations $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$}
{$s \to^* s'$ ? \\}

\problemx{$d$-VASS zero reachability}
{Vass $V=(Q,T)$, $q(\textbf{v}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{v}) \to^* p(\textbf{0})$? \\}

@@

A {\em reset ... }
Reset VASS are VASS extended with reset transitions.

\problemx{Reset $d$-VASS reachability}
{A reset $d$-Vass $d$-Vass $V=(Q,T)$, $s,s' \in Q \times \N^d$}
{$s \to^* s'$ ? \\}

\problemx{Reset $d$-VASS zero reachability}
{A reset $d$-Vass $V=(Q,T)$, $q(\textbf{u}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{u}) \to^* p(\textbf{0})$? \\}

>>>>

\iffalse
\mathieu{ Maybe add this back ?
A {\em labeled transition system} (LTS for short) is a tuple $\mathscr{S}=(S, \Sigma, \rightarrow)$ where 
$S$ is a set of {\em states}, $\Sigma$ is a (finite) set of {\em labels}, and 
${\rightarrow} \subseteq S\times \Sigma \times S$ is a 
ternary relation,
denoted as the set of {\em labeled transitions}. }
\fi
\end{definition}

@@

\problemx{$d$-VASS reachability}
{A $d$-VASS $V=(Q,T)$, and configurations $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$}
{$s \to^* s'$ ? \\}

\problemx{$d$-VASS zero reachability}
{VASS $V=(Q,T)$, $q(\textbf{v}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{v}) \to^* p(\textbf{0})$? \\}

@@

Reset VASS extend the basic VASS model with special “reset
arcs” that resets (set to $0$) some coordinates in the vector. \\

More Formally {\em reset ... }

\begin{samepage}
\problemx{Reset $d$-VASS zero reachability}
{A reset $d$-VASS $V=(Q,T)$, $q(\textbf{u}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{u}) \to^* p(\textbf{0})$? \\}
\end{samepage}
